My title

### 2024-02-11 outputs/paper/paper.qmd
paper updated

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Ziheng Zhong
  - Charles Cai
thanks: "Code and data are available at: https://github.com/iJustinn/Effect_of_Charter_Schools_on_School_Segregation.git"
date: today
date-format: long
abstract: "Write after we have the results"
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
```

@@

# Results

# Discussion

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Ziheng Zhong
  - Charles Cai
thanks: "Code and data are available at: https://github.com/iJustinn/Effect_of_Charter_Schools_on_School_Segregation.git"
date: today
date-format: long
abstract: "Write after we have the results"
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(ggplot2)
library(janitor)
library(dplyr)
library(readr)
library(knitr)
```

@@

# Results {#sec-res}

# Discussion {#sec-dis}
